Prediction of 90-day mortality after Total Hip Arthroplasty: a simplified and externally validated model based on Swedish and English register data

### 2019-09-24 reports/article.Rmd
changed everything except report after implementing BRLasso

---
title: "Prediction of 90-day mortality after Total Hip Arthroplasty: a simplified and extrenaly validated model based on Swedish and English register data"
author: Anne Garland^1,2,3^, Erik Bulow^2,4^, Adrian Sayers^5,6^, Szilard Nemes^2,4^, Ola Rolfson^2,4^, Nils P. Hailer^1,2^
date: '2019-03-12'
bibliography: P:/library.bib
output: 
  bookdown::word_document2:
    toc: false
    df_print: kable
---

>>>>

---
title: "Prediction of 90-day mortality after Total Hip Arthroplasty: a simplified and externally validated model based on Swedish and English register data"
author: Anne Garland^1,2,3^, Erik Bulow^2,4^, Adrian Sayers^5,6^, Szilard Nemes^2,4^, Ola Rolfson^2,4^, Nils P. Hailer^1,2^
date: '2019-03-12'
bibliography: P:/library.bib
output: 
  bookdown::word_document2:
    toc: false
    df_print: kable
---
